---
title: "Final project"
author: "Yuki Wang"
date: "Fall 2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

run the following codes to get started
```{r}
library(XML)
library(tidyverse)
library(rvest)
library(lubridate)
library(readxl)
library(cowplot)
library(ggplot2)
library(stringr)
library(stargazer)
```

## 1. Scrape information from the IMF website, organize this data into a dataframe see the voting power of all member states.

scrap from the "IMF Members' Quotas and Voting Power, and IMF Board of Governors" to get the current voting power of member states https://www.imf.org/external/np/sec/memdir/members.aspx#Z
```{r}
#get page link
page_link <- paste0("https://www.imf.org/external/np/sec/memdir/members.aspx")
  
#read the search page
voting <- read_html(page_link) 

#write a function to get all the charts in the link
number <- function(i){
  table_votes <- html_table(html_nodes(voting, "table"),fill = TRUE,header=TRUE)[[i]]
  return(table_votes)
  }
votes <- map_dfr(5:28,number)
  
# rename the columns
names(votes)
votes <- votes %>%
  rename(country =...1,
         vote_numbers =VOTES...5,
         vote_percentage = VOTES...6) 

# To make further calculation, we need to convert 'vote_percentage' to numeric vectors
  votes$vote_percentage <- as.numeric(votes$vote_percentage)

# make the dataset cleaner 
  votes <- votes %>%
    select(country,vote_percentage) %>%
    arrange(country)%>%
    na.omit()
  head(votes)
# write the dataframe to a csv file. 
write_csv(votes,"votes.csv")
```


## 2. a statistical analysis of IMF quota and voting rights reform. 

import the dataset 'quotas.xlsx' and make some preliminary calculation 
```{r}
quotas <- read_excel("/Users/yuki/Desktop/PLSC 31101/assignments/Final project/data/quotas.xlsx", sheet = 1) 

quotas <- quotas %>%
  # select columns with calculated quotas
  select(country,cal_before,cal_review,cal_previous,cal_current) %>%
  arrange(country)

# To make further calculation, we need to convert certain columns to numeric vectors
quotas$cal_before <- as.numeric(quotas$cal_before)
quotas$cal_review <- as.numeric(quotas$cal_review)

# calculate quota growth rates during each period of each country,and define them as new variables
quotas <- quotas %>%
  mutate(round1 = (cal_review - cal_before)/ cal_before,
         round2 = (cal_previous- cal_review)/ cal_review,
         round3 = (cal_current - cal_previous)/ cal_previous,
         total = (cal_current - cal_before)/cal_before) 
head(quotas)
```

separate three rounds and analyze each of them to find main member countries in the reforms. 

```{r}
# The first round was from June 2006 - April 2008.
group1 <- quotas %>%
  select(country,round1,cal_before)%>%
  filter(!is.na(round1)) %>%# remove NAs 
  filter(!is.na(cal_before)) %>%# remove NAs 
  arrange(-(round1))
  # find the countries with the highest and lowest quota growth rate during the first round of reform
positive_group1 <- top_n(group1,30,round1)
negative_group1 <- top_n(group1,-30,round1) %>%
  arrange(round1)

  # countries with the highest quota growth rate during the first round reform are all developing countries except Iceland, but countries with the lowest growth rate are not necessarily developed countries. There are also many low-income countries in Africa,which indicates that the first round reform did not improve the status of these countries.

# The second round was from August 2009—July 2012.
group2 <- quotas %>%
  select(country,round2,cal_review)%>%
  filter(!is.na(round2)) %>%# remove NAs 
  filter(!is.na(cal_review)) %>%# remove NAs 
  arrange(-(round2))

positive_group2 <- top_n(group2,30,round2)
negative_group2 <- top_n(group2,-30,round2) %>%
  arrange(round2)
  # countries with the highest quota growth rate during the second round reform are all developing countries now 

# The third round was from August 2011—January 2013, but it is not until January 21, 2016 that the proposed amendment on reform of the Executive Board came into force.
group3 <- quotas %>%
  select(country,round3,cal_previous)%>%
  filter(!is.na(round3)) %>%# remove NAs 
  filter(!is.na(cal_previous)) %>%# remove NAs 
  arrange(-(round3))
positive_group3 <- top_n(group3,30,round3)
negative_group3 <- top_n(group3,-30,round3)%>%
  arrange(round3)
# Ireland is a special case

```

Create a new dataframe to analyze three rounds of reform together to see the general trend
```{r}
mean1_pq = mean(positive_group1$cal_before)
mean1_pg = mean(positive_group1$round1)
mean1_nq = mean(negative_group1$cal_before)
mean1_ng = mean(negative_group1$round1)
mean2_pq = mean(positive_group2$cal_review)
mean2_pg = mean(positive_group2$round2)
mean2_nq = mean(negative_group2$cal_review)
mean2_ng = mean(negative_group2$round2)
mean3_pq = mean(positive_group3$cal_previous)
mean3_pg = mean(positive_group3$round3)
mean3_nq = mean(negative_group3$cal_previous)
mean3_ng = mean(negative_group3$round3)

vec_1 <- c("round1","round2","round3")
vec_2 <- c(mean1_pq,mean2_pq,mean3_pq,mean1_nq,mean2_nq,mean3_nq)
vec_3 <- c(mean1_pg,mean2_pg,mean3_pg,mean1_ng,mean2_ng,mean3_ng)
vec_4 <- c("highgrowth30","highgrowth30","highgrowth30","lowgrowth30","lowgrowth30","lowgrowth30")
quota_growth <- data.frame(vec_1,vec_2,vec_3,vec_4)
colnames(quota_growth) <- c("round","avg_quota","avg_rate","type")

p1 <- quota_growth %>%
  ggplot(aes(x=round, y=avg_quota, color=type))+
  geom_point(size=1.5)+
  labs(title="Average Quotas Over time", #title 
       x="reform", #x axis
       y="Average Quota")+ #y axis
  #adjut title, axies, legends
  theme(axis.text.x = element_text(size=5), 
        axis.title.x = element_text(size=8), 
        axis.title.y = element_text(size=8),
        plot.title=element_text(size=8), 
        legend.key.size = unit(0.3, "cm"), 
        legend.title = element_text(size=8), 
        legend.text = element_text(size=5)) 

p2 <- quota_growth %>%
  ggplot(aes(x=round, y=avg_rate, color=type))+
  geom_point(size=1.5)+
  labs(title="Average Growth Rate Over time", #title 
       x="reform", #x axis
       y="Average Growth Rate")+ #y axis
  #adjut title, axies, legends
  theme(axis.text.x = element_text(size=5), 
        axis.title.x = element_text(size=8), 
        axis.title.y = element_text(size=8),
        plot.title=element_text(size=8), 
        legend.key.size = unit(0.3, "cm"), 
        legend.title = element_text(size=8), 
        legend.text = element_text(size=5)) 

cowplot::plot_grid(p1,p2,nrow = 1,ncol = 2) 

```
Focus on all the member states
```{r}
ggplot(quotas, aes(x=cal_before, y=total))+
  geom_point(size=0.5)+
  scale_x_log10()+
  scale_y_log10()+
  labs(title="Quota growth rate by Quota, 2006-2016", 
       x="Quotas before the first round reform", 
       y="Quota growth rate during the three rounds of reform")+
  geom_smooth(color="red", fill="red", size =0.5)+ 
    #adjust axis, title and legend
  theme(axis.text.x = element_text(size=5), 
        axis.title.x=element_text(size=8), 
        axis.title.y = element_text(size=5), 
        axis.text.y = element_text(size=5),
        plot.title=element_text(size=8), 
        legend.key.size = unit(0.3, "cm"), 
        legend.title = element_text(size=5),
        legend.text = element_text(size=5)) 

```

Focus on the largest shareholders

```{r}
powers <- quotas %>%
  select(country,cal_before,cal_current,total) %>%
  arrange(-(cal_current)) 
greatpowers1 <- top_n(powers,10,cal_current)

powers <- quotas %>%
  select(country,cal_before,cal_current,total) %>%
  arrange(-(cal_before)) 
greatpowers0 <- top_n(powers,10,cal_before)

vec_5 <- c("developed","developing","developed","developed","developed","developing","developed","developing","developed","developing")
attach(greatpowers1)
greatpowers1$type <- vec_5

vec_6 <- c("developed","developed","developing","developed","developed","developed","developed","developed","developed","developed")
attach(greatpowers0)
greatpowers0$type <- vec_6

p3 <- greatpowers0 %>%
  ggplot(aes(x=country, y=total,fill=type))+
  geom_col()+ 
  #change color
  scale_fill_manual(values=c("#771C19", "#E25033"))+ 
  labs(title="Quota growth rate of 2006top10", #title
       x="Country", 
       y="Quota Growth Rate")+ 
  #rotate the x axis title and change its size and position
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, size=5), 
  #adjust axis, title and legend
        axis.title.x = element_text(size=8), 
        axis.title.y = element_text(size=5), 
        plot.title=element_text(size=8), 
        legend.key.size = unit(0.3, "cm"), 
        legend.title = element_text(size=8), 
        legend.text = element_text(size=8)) 

p4 <- greatpowers0 %>%
  ggplot(aes(x=country, y=cal_before,fill=type))+
  geom_col()+ 
  #change color
  scale_fill_manual(values=c("#771C19", "#E25033"))+ 
  labs(title="Quota shares of 2006top10", #title
       x="Country", 
       y="Quota shares 2006")+ 
  #rotate the x axis title and change its size and position
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, size=5), 
  #adjust axis, title and legend
        axis.title.x = element_text(size=8), 
        axis.title.y = element_text(size=5), 
        plot.title=element_text(size=8), 
        legend.key.size = unit(0.3, "cm"), 
        legend.title = element_text(size=8), 
        legend.text = element_text(size=8)) 

p5 <- greatpowers1 %>%
  ggplot(aes(x=country, y=total,fill=type))+
  geom_col()+ 
  #change color
  scale_fill_manual(values=c("#771C19", "#E25033"))+ 
  labs(title="Quota growth rate of 2016top10", #title
       x="Country", 
       y="Quota Growth Rate")+ 
  #rotate the x axis title and change its size and position
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, size=5), 
  #adjust axis, title and legend
        axis.title.x = element_text(size=8), 
        axis.title.y = element_text(size=5), 
        plot.title=element_text(size=8), 
        legend.key.size = unit(0.3, "cm"), 
        legend.title = element_text(size=8), 
        legend.text = element_text(size=8)) 

p6 <- greatpowers1 %>%
  ggplot(aes(x=country, y=cal_current,fill=type))+
  geom_col()+ 
  #change color
  scale_fill_manual(values=c("#771C19", "#E25033"))+ 
  labs(title="Quota Shares of 2016top10", #title
       x="Country", 
       y="Quota Shares 2016")+ 
  #rotate the x axis title and change its size and position
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, size=5), 
  #adjust axis, title and legend
        axis.title.x = element_text(size=8), 
        axis.title.y = element_text(size=5), 
        plot.title=element_text(size=8), 
        legend.key.size = unit(0.3, "cm"), 
        legend.title = element_text(size=8), 
        legend.text = element_text(size=8)) 

cowplot::plot_grid(p3,p4,p5,p6,nrow = 2,ncol = 2)

```


## 3. an empirical analysis of the effects of quota reform on voting rights and IMF conditionality. 

import the dataset 'arrangement' and form a new dataset 'conditionality'(the dependent variable)

```{r}
arrangement <- read_excel("/Users/yuki/Desktop/PLSC 31101/assignments/Final project/data/arrangement.xlsx", sheet = 1) 

conditionality <- arrangement %>%
  filter(Conditionality == "Yes") %>%
  select(country,ArrID,ArrType,IniPgmYr,BoardActDate,ReviewType,TotalAccess,Comments) %>%
  filter(IniPgmYr<2017) %>%
  group_by(country) %>%
  count(country) %>%
  rename(conditionality = n)
head(conditionality)
# the dependent variable is the number of types of conditionality of a member state
  
```

import the dataset 'CV'(control variables) and 'DV1_votes'(the first dependent variable)
```{r}
CV <- read_excel("/Users/yuki/Desktop/PLSC 31101/assignments/Final project/data/CV.xlsx", sheet = 1)

DV1_votes <- read_excel("/Users/yuki/Desktop/PLSC 31101/assignments/Final project/data/DV1_votes.xlsx", sheet = 1)

```

merge the datasets and run the regression model

```{r}
factors <- CV %>%
    #use inner_join to keep all observations 
  inner_join (quotas,by = c("country"))  

merge1 <- factors %>%
  inner_join(DV1_votes,by = c("country")) %>%
  rename(gdpPercap = `GDP per capita`,
         reserves_debt = `Total reserves (% of total external debt)`,
         FDI = `Foreign direct investment, net inflows`,
         IMFcredit = `Use of IMF credit`,
         account_balance = `Current account balance`,
         quotas2006 = cal_before,
         votes2016 = vote_percentage) %>%
  select(country,gdpPercap,reserves_debt,FDI,IMFcredit, account_balance,quotas2006,votes2016)

merge2 <- merge1 %>%
  inner_join(conditionality,by = c("country"))

#model1: only one independent variable,investigating the relationship between quotas before the reform and votes after the reform
mod1<-lm(votes2016~quotas2006, data=merge1) 
#model2: including all control variables
mod2<-lm(votes2016~log(gdpPercap)+reserves_debt+FDI+IMFcredit+account_balance+quotas2006, data=merge1) 
#model3: only two independent variables, investigating th quotas and votes' influence on the IMF conditionality on member states
mod3<-lm(conditionality~quotas2006+votes2016, data= merge2)
#model3: including all control variables
mod4<-lm(conditionality~log(gdpPercap)+reserves_debt+FDI+IMFcredit+account_balance+quotas2006+votes2016, data=merge2) 

stargazer(mod1, mod2,mod3,mod4,
          title = "Regression Results1",
          type = "text",
          dep.var.labels = "DV: Voting Rights", 
          #remove and keep targeted results 
          omit="Constant", 
          keep.stat="n",
          style="ajps", 
          #write the file
          out="regression-table1.txt")
```

